### 2011-07-07 Paper/Paper.tex
HMM now works as it should. Last commit broke that #%@! alignment again

>>>>

Although certainly not all expression is at structural level we may plausibly assume that \emph{something} is happening at structural level. The goal is to capture this dimension of expression in a performance rendering system. The resulting performances will demonstrate that expression at structural level is can be extracted and is meaningful
